---
title: "Exercise 12.5"
author: ""
date: ""
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 

# Some customization.  You can alter or delete as desired (if you know what you are doing).
trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

## Exercise 12.5

Import data set for Exercise 12.5:
```{r}
power <- read.table("https://asta.math.aau.dk/datasets?file=power.txt", header = TRUE)
head(power)
```

The dataset contains the following variables:
- `consumption`: The monthly electrical power consumption of a chemical plant.
- `temperature`: The ambient temperature.
- `days`: The number of active days in the month.
- `purity`: The average product purity.
- `production`: The tons of product produced.

Fit a multiple regression model with `consumption` as the response and `temperature`, `days`, `purity`, `production` as predictors and answer the following questions:
  - Write down the prediction equation.
  - What is the effect on the predicted response if the production is increased by 1 ton while all other variables are kept fixed?
  - What is the interpretation of the intercept?
  - Find R-squared. What is the interpretation of this?
  - Make an overall F-test for the null-hypothesis that there is no effect of any of the predictors. What is your conclusion?
  
First we fit the data to a linear model using lm
```{r}
model <- lm(consumption ~ temperature+days+purity+production, data = power)
summary(model)
```
The prediction equation is given as $\hat{y} \approx a+b_1x_1+b_2x_2+b_3x_3+b_4x_4$
$\rightarrow \hat{y} \approx -102.713+0.605x_1+8.924x_2+1.437x_3+0.014x_4$

The result on the predicted response, if all variables are fixed but production is x_4 pr. unit, and as we increase by
1 unit, the increase is 1 ton, assuming that production is in tons, the prediction is increased by 1*0.014 = 0.014.

The intercept indicates the response when all variables are at zero. An example could be a 4-20 mA load cell, where the intercept 
is the output current of the load cell when no load is applied to it.
In this case, it will be the consumption when temperature is 0, days is 0, purity is 0 and production is 0. 
It is the mean response when all predictors are equal to zero

In our case, when when all predictor but x4 are kept fixed, we get a new intercept given as
$\tilde{a} = a +b_1x_1+b_2x_2+b_3x_3$
So one could imagine that if we "freeze frame" at some predictor values of all but x4, the intercept would be the baseline, such that
the intercept would be the consumption with all these fixed predictors, and varying x4 around 0 allows us to see how this baseline
consumption varies with the predictor not fixed.

R-squared is 0.745, as found in the summary of the model.
```{r}
anova(model)
```
The ANOVA test compares the populations means. It is an analysis of variance, and as such is F-distributed. We see that temperature
clearly has an effect, as we cannot prove it wrong under the null hypothesis that it has no influence, all the others can more
or less be seen as being explained by statistical sampling.


