\section{Requirement Review} \label{subsec:8_1_ReqReview}

All of the requirements from table \refq{tab:5_SystemRequirements} have been reviewed in order to see if the product meets the specifications.


\subsubsection*{Requirement §1: Frequency range}
The system must be capable of generating sine waves from \SIQ{50}{\hertz} to \SIQ{1}{\mega\hertz} with a resolution of \SIQ{1}{\hertz}.

\textbf{Status:} The DAC is controlled by a DDS block in the Sample Control Module, at a sample rate of \SIQ{20}{\mega\hertz}. The DDS block has a resolution of \SIQ{4.657}{\milli\hertz}, essentially allowing the DAC to generate frequencies down to \SIQ{4.657}{\milli\hertz}. The reconstruction filter however is AC coupled with a simulated lower cut-off of less than \SIQ{10}{\hertz}. The upper cut-off frequency for the reconstruction filter is simulated to more than \SIQ{1.5}{\mega\hertz}. The actual pass-band of the system has been tested to be \SIQ{10}{\hertz} to \SIQ{1.23}{\mega\hertz}, see appendix \ref{subsec:BW_Test}. The resolution has been tested to be at least \SIQ{1}{\hertz}. This requirement is met.
\nl
\nl

\subsubsection*{Requirement §2: Impedance Fit}
Impedance fit to either series model or parallel model.

\textbf{Status:} This is implemented in software, the functionality is shown in section \refq{sec:MCU}.
\nl
\nl

\subsubsection*{Requirement §3: Impedance Range}
The instrument should be able to measure an impedance in the interval $10m\Omega < |Z| < 100M \Omega$. 

\textbf{Status:} This has been tested and the results can be seen in appendix \refq{App:AccuracyBWTest}. The test results are very promising, but ultimately inconlusive. The proper test equipment was not available to perform this test.
\nl
\nl

\subsubsection*{Requirement §4 and §5: Modulus and Argument accuracy}
The specific requirement can be seen in section \refq{sec:ModulusArgumentAccuracy}.

\textbf{Status:} The instrument accuracy has been tested at varies impedances and frequencies, no higher than \SIQ{300}{\kilo\hertz}, these tests can be seen in appendix \refq{App:AccuracyBWTest}. A review of this can be seen in section \refq{subsec:8_1_AccTest}. These requirements are not met.
\nl
\nl

\subsubsection*{Requirement §6: Test voltage Range}
It must be possible to set the test voltage in the range of \SIQ{10}{\milli\volt}$_{pp}$ to \SIQ{10}{\milli\volt}$_{pp}$ with a resolution of \SIQ{10}{\milli\volt}.

\textbf{Status:} It is only possible to set the test voltage at 4 fixed levels, \SIQ{0.6}{\volt}$_{pp}$, \SIQ{1.2}{\volt}$_{pp}$, \SIQ{2.3}{\volt}$_{pp}$ and \SIQ{4.3}{\volt}$_{pp}$. This requirement is not met.
\nl
\nl

\subsubsection*{Requirement §7: Maximum Test Current}
The system must be capable of generating a minimum current of \SIQ{100}{\milli\ampere}$_{pp}$.

\textbf{Status:} The system has been found capable of delivering more than \SIQ{105}{\milli\ampere}$_{pp}$, see appendix \ref{subsec:MaxCurrent}. The designed system meets this requirement.
\nl
\nl

\subsubsection*{Requirement §8: DC Bias Voltage Range}
The system should be capable of biasing the DUT to a voltage in the range of \SIQ{0}{\volt} to \SIQ{20}{\volt}.

\textbf{Status:} No biasing system has been designed and as such the system cannot generate any DC bias voltage. This requirement is not met.
\nl
\nl

\subsubsection*{Requirement 9: Parameters of DUT}
The system should be able to indicate the following DUT parameters:
\begin{itemize}
    \item $L$
    \item $C$
    \item $R$
    \item $Q$
    \item $D$
    \item $R_s$
    \item $R_p$
    \item $Z$ and $\phi$
\end{itemize}

\textbf{Status:} All these parameters can be calculated from the complex impedance. This requirement is met.
\nl
\nl

\subsubsection*{Requirement §10: Parameter Sweep}
The system should be capable of performing frequency and DC bias voltage sweeps.

\textbf{Status:} The system can perform frequency sweeps but the functionality has not been implemented. No biasing circuit has been implemented so no bias sweeps can be performed. This requirement is not met.
\nl
\nl

\subsubsection*{Requirement §11: Frequency Sweep Range}
The frequency sweep range of the system should be \SIQ{50}{\hertz} to \SIQ{1}{\mega\hertz}.

\textbf{Status:} The system can perform frequency sweeps and generate frequencies within the given range, but the functionality has not been implemented. This requirement is not met.
\nl
\nl

\subsubsection*{Requirement §12: Maximum Frequency Sweep Points}
The system should be able to store 10000 points in a single frequency sweep.

\textbf{Status:} No sweep functionality has been implemented, this requirement is not met.
\nl
\nl

\subsubsection*{Requirement §13: Maximum Frequency Sweep Points}
The system should be able to store 100 points in a single bias voltage sweep.

\textbf{Status:} No sweep functionality has been implemented, this requirement is not met.
\nl
\nl

\subsubsection*{Requirement §14: Binning}
The system should be capable component binning as explained in section \ref{sec:5_1_Binning}.

\textbf{Status:} No binning functionality has been implemented, this requirement is not met.
\nl
\nl

\subsubsection*{Requirement §15: Histogram}
The system should be able to generate and plot a histogram of measured values.

\textbf{Status:} No histogram function has been implemented, this requirement is not met.
\nl
\nl

\subsubsection*{Requirement §16: Plots}
The system should be capable of plotting the measured parameters vs. frequency and bias voltage.

\textbf{Status:} No sweep functionality has been implemented, this requirement is not met.
\nl
\nl

\subsubsection*{Requirement §17: Interface}
The system must have a 7" touch screen.

\textbf{Status:} The system has a 7" touch screen, this requirement is met.
\nl
\nl

\subsubsection*{Requirement §18: DUT Connection}
The system should use a 4-wire kelvin connection to connect to the DUT.

\textbf{Status:} The system uses a shielded 4-wire kelvin connection, this requirement is met.
\nl
\nl

\subsubsection*{Requirement §19: Data Export}
The system should be able to export data to a CSV file via UART.

\textbf{Status:} The system can export data via UART, this requirement is met.
\nl
\nl

