---
title: "Exercises 11.1, 11.15, 11.44"
author: ""
date: ""
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
library(mosaic)
# Some customization.  You can alter or delete as desired (if you know what you are doing).
trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

## Exercise 11.1, 11.15, 11.44

Import data set for Exercise 11.1:
```{r}
strength <- read.table("https://asta.math.aau.dk/datasets?file=strength.txt", header = TRUE)
head(strength)
```

You should answer the exercise by an analysis in RStudio.

Start by making relevant plot(s).
```{r}
## Write plot command(s) here. Hint: gf_point could be relevant...
gf_point(dynamicLift ~armStrength, data = strength)
```

Then fit the linear model in R:

```{r}
model = lm( dynamicLift ~ armStrength, data = strength)
summary(model)
```

Now answer questions 11.1 (a) - (b) and 11.15.
We can read the slope and intercept directly from the linear model, here we find them to be
11.1 (a)
b0 = intercept = 64.3944
b1 = slope = 0.5645
```{r}
b0 <- 64.3944
b1 <- 0.5645
```

11.1 b
We evaluate the function at x = 30, and get $\mu_{y|30} = 64.3944+30*0.5645$
```{r}
b0+b1*30
```
11.15 a
```{r}
res<- resid(model)
SSE <- sum(res^2)
s_sq <- SSE/(length(res)-2)
s_sq
```
11.15 b
To test that the true b0 = 0, we say that H0: b0 = 0 and test this.
the linear model gives this output directly in the sumary and we can see that it has a probability of 0.0515 with a 
t-score of 2.054.
We do not have enough evidence to reject H0, and thus we cannot say with 95% certainty that there is a correlation from x to y.


You can visualize the regression line by filling out the following code:
```{r}
plotModel(model)
```



In Exercise 11.44 (a), you need to find the correlation.
```{r}
## Write a command like: cor( ??? )
r <- cor(dynamicLift ~ armStrength, data = strength)
r
```

What does this correlation tell you?
It gives a measure of how much y and x correlate. It is standardized to the standard deviation of the y and x axis, making it
indefferent to any changes in "numeric" value. r = 1 means they completly correlate, -1 means the same but for a falling slope etc.

Find $R^2$ and interpret the result.
R squared in this case of only one input variable is simply the correlation coeffecient squared
thus we get
```{r}
r_sq <-r^2
r_sq
```

